### 2019-11-09 ch9_guidelines/content.tex
rename chapters

\section{Introduction}

Many fields of computational research are characterized by a growing number of available methods for data analysis. For example, at the time of writing, almost 400 methods are available for analysing data from single-cell RNA-sequencing experiments \cite{zappia_exploringsinglecellrnaseq_2018}. For experimental researchers and method users, this represents both an opportunity and a challenge, since method choice can significantly affect conclusions.

@@

The review is structured as a series of guidelines (Figure \ref{fig:summary_guidelines}), each explained in detail in the following sections. We use examples from computational biology; however, we expect that most arguments apply equally to other fields. We hope that these guidelines will continue the discussion on benchmarking design, as well as assisting computational researchers to design and implement rigorous, informative, and unbiased benchmarking analyses.

>>>>

% GUIDELINES FOR BENCHMARKING

\section{Introduction}
Many fields of computational research are characterized by a growing number of available methods for data analysis. For example, at the time of writing, almost 400 methods are available for analysing data from single-cell RNA-sequencing experiments \cite{zappia_exploringsinglecellrnaseq_2018}. For experimental researchers and method users, this represents both an opportunity and a challenge, since method choice can significantly affect conclusions.

@@

\section{Ten essential guidelines}
The review is structured as a series of guidelines (Figure \ref{fig:summary_guidelines}), each explained in detail in the following sections. We use examples from computational biology; however, we expect that most arguments apply equally to other fields. We hope that these guidelines will continue the discussion on benchmarking design, as well as assisting computational researchers to design and implement rigorous, informative, and unbiased benchmarking analyses.
